On particular examples of planar integral point sets and their classification \footnote{ This work was carried out at Voronezh State University and supported by the Russian Science Foundation grant 19-11-00197. }

### 2021-02-24 AvdMomZvolA_examples/ips_examples.tex
[AMZAE] One more sophisticated example

%TODO: 8_2535_1_d680ff2d172ebe40250a54ca9419af34

>>>>

Figure~\ref{8_2535_1_d680} displays an IPS with
no axis of symmetry;
alothough the set is of characteristic 1,
it cannot be extended by reflecting relatively to the $x$ axis.
Moreover, we failed to extend it by dilation and looking for extra points on the $x$ axis.

%TODO: write about points which prevent the set from reflection

$\mathcal{P}_8=
\sqrt{1}/13*
\{
( 29575 ; 0);
( -2366 ; -8112);
( 12844 ; 0);
( 10647 ; -14196);
( 8450 ; 0);
( 15022 ; -3696);
( 21294 ; 0);
( 0 ; 0);
\}
$

\begin{figure}[h!]
\center{\includegraphics[width=1\linewidth]{./img/8_2535_1_d680ff2d172ebe40250a54ca9419af34_other.png}}
\parbox{1\linewidth}{\caption{IPS of cardinality 8 and diameter 2535}
\label{8_2535_1_d680}}
\end{figure}
